---
title: "ROOP Static Variable"
author: "Kevan Doyle"
date: "January 23, 2015"
output: html_document
---

### Bottom line
For a static variable in a function that will be constructed only once, wrap the function in a constructor and return a list with a getter and setter of the static variable and the function you want to use.

To include a static variable in a class that will be used to create multiple objects, wrap the object constructor inside a class constructor that contains the static variable and that will be called only once (so there is a nest of class constructor that returns the object constructor that returns objects which are a list containing variables, setters, getters and methods)

### How to make an object with a static variable
````{r echo=FALSE}
library(knitr)
read_chunk('ROOP_StaticVariable.R')
```

### Function that creates a class that will hold the static variable
````{r echo=TRUE,label='class maker'}
<<parent function>>
```

### The actual function you will use in your code
```{r echo=TRUE,label='the func with static variable'}
<<the function to use>>
```

### Check that the variable is indeed static
```{r echo=TRUE,label='check that var is static'}
myfunc$getstatv()
myfunc$setstatv(42)
myfunc$getstatv()
```

### An Application: a function that counts how many times it has been called

